%\documentclass[10pt, a4paper, twocolumn, fleqn]{article}
\documentclass[10pt, a4paper, onecolumn, fleqn]{article}
\usepackage{amsmath}
\usepackage{geometry}
%\geometry{top=3.5cm,bottom=3cm}
%\geometry{left=2.5cm,right=2.8cm,top=3.5cm,bottom=3cm}
\geometry{left=2cm,right=2cm,top=2.5cm,bottom=2.5cm}

\begin{document}
\title{A Study of Network Protocol Evolution}
\author{Li Jiaying, Dong Fei}
\maketitle

\pagestyle{empty}
\section*{Abstract}
In FAST'13, a paper named ``A study of Linux File System Evolution'' from University of Wisconsin, Madision won the best paper prize. It talks about changes of several file-systems in a period of the Linux history. The author analysed eight years of Linux file-system changes across 5079 patches to derive numerous new insight into the file-system development process, which can be very useful for both both the development of file systems themselves as well as the improvement of bug-finding tools. 

In the networking course project, we would like to apply the same approach to some network protocols, that means we want to analyze fome linux network protocol changes in the early years of linux, and then look into these results to get an insight into the network development process. We hope we could conduct this project successfully, and draw the conclusion which is useful for people who develop network protocols and for the people who create bug-finding tools for network protocols.



\section{Introduction}
Just by having a rough look at the RFC directory, and we can conduct that more and more network protocols come into birth nowadays, and there is an obvious tendency that this process is speedup.
These protocols remain a moving target. Developed by different teams with different goals , these network protocols evolve repidly to add new features, fix bugs, and improve performance and reliability. Major new network protocol are introduced every few years, and with technology and infrastructure changes in recent years, we can expect even more flux in this domain without any doubt.


\section{Goals}
We want to ....


\section{process}
We would like to achive the above goal through the following ways:
\begin{enumerate}
\item[-]We analyze ...
\item[-]We find out ...
\item[-]We can draw conclusion that ...
\end{enumerate}



\section{Bibiograph}
[1]Lanyue Lu, Andrea C. Arpaci-Dusseau, et. al, ``A Study of Linux File System Evolution''. in FAST'13.
\newline
[2]Lidia Yamamoto, Christian Tschudin, ``Generic Evolution of Protocol Implementations and configurations'', IFIP/IEEE INTERNATIONAL WORKSHOP ON SELF-MANAGED SYSTEMS AND SERVICES.
\newline
[3]Micheal Hicks, Scott Nettles, ``Active Networking Means Evolution (or Enhanced Extensibility Required)''.
\newline
[4]``THINK protocols'', $http://www.cs.utexas.edu/users/chris/think/digital\_archive.html.$

\end{document}
