%\documentclass[10pt, a4paper, twocolumn, fleqn]{article}
\documentclass[10pt, a4paper, onecolumn, fleqn]{article}
\usepackage{amsmath}
\usepackage{geometry}
%\geometry{left=2.5cm,right=2.8cm,top=3.5cm,bottom=3cm}
\geometry{left=2cm,right=2cm,top=2.5cm,bottom=2.5cm}

\begin{document}
\title{Proposal: A Survey on P2P Network}
\author{Li Jiaying, Dong Fei}
\maketitle

\pagestyle{empty}
\section{Research Title and Theme}
Proposal: A Survey on P2P Network.
P2P has been in use for about 15 years.
There are many problems and chanlenges P2P encountered in these years.
And reserchers and engineers has come out many approach to those problems.
We want to do a survey on the problems brought by P2P, and its solutions.


\section{Research Context}
It has been a controversial topic since it first come into public view in 1999.
The convenience for sharing resource brought by P2P softwares excite customer,
but its big current flow is a nightware to ISPs, and other network companies.
It can also cause copyright problems, which make many countries cut off the P2P current.

\section{Aims and Objectives}
Through this survey we want to get to know the evolution history of P2P, both in scientific areas and in industrial companies.
We would like to classify the topics around P2P, and make it easy for people to know how P2P changes.
And the other objective is we want to predict where P2P would go in the future.


\section{Methodology}
We would like to achive the above goal through the following ways: \begin{enumerate}
\item[-]We analyze ...
\item[-]We find out ...
\item[-]We can draw conclusion that ...
\end{enumerate}


\section{Expected Results and Implication of Results}




\section{References}



\end{document}
